---
title: "Malaria"
author: "Tilina Alzaben"
date: '2022-06-09'
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2)
library(dplyr)
library(tidytext)
library(gsheet)
library(wordcloud2)
library(sentimentr)
library(lubridate)
library(readr)
library(knitr)
```

# Malaria Dataset
```{r}
pms <- read_csv('https://github.com/databrew/intro-to-data-science/blob/main/data/pms.csv?raw=true')

kable(head(pms))
```

# Introduction 
Regarding Malaria cases in Mozambique, we will identify the change in number of cases from January to December of 2021.

# Methods 
```{r}
month <- pms %>% filter(date_visit >= '2021-01-01' & date_visit < '2022-01-01') %>% mutate(mnth = month(date_visit))

cases <- month %>% filter(malaria_diagnosis == "Malaria") %>% group_by(mnth) %>% tally()

kable(cases)

ggplot(data = cases) +
  geom_line(aes(x=mnth, y=n)) + 
  scale_x_continuous(breaks = 1:12, labels = month.abb) + 
  labs(title = 'Number of Malaria Cases in 2021', 
       x = 'Month', y = 'Number of Cases')
```

# Results
We can see that there is a rapid increase in the number of cases from January to April, reaching more than 8000. Shortly after, the number of cases drop down to a little over 5000 at June, but then continue to increase up to October. As the season moves to winter, the number of cases rapidly decrease. 


